|

### 2021-09-20 01-Chp-Background.Rmd
End of day:

Given the substantial burden that dementia represents and the absence of any curative therapies, as detailed in the above sections, the assessment of easily modifiable targets for their utility in the prevention of dementia should be prioritized.[@winblad2016a] To date, a substantial amount of research has been produced examining putative risk factors for dementia.[@feingold2000;@peters2019; @ansteya]

@@

Several previous systematic review of observational studies examining the effect of lipids[@anstey] and lipid-regulating agents[@chu2018b;@poly2020c] on dementia outcomes have been performed. However, these reviews have several limitations. Many did not consider grey literature sources (see Section \@ref(diverse-sources-preprints)). Additionally, many of the reviews of observational studies did not perform any risk-of-bias assessment[@chu2018b] or used an outdated assessment tool.[@anstey;@poly2020c]

>>>>

Given the substantial burden that dementia represents and the absence of any curative therapies, as detailed in the above sections, the assessment of easily modifiable targets for their utility in the prevention of dementia should be prioritized.[@winblad2016a] To date, a substantial amount of research has been produced examining putative risk factors for dementia.[@feingold2000;@peters2019; @anstey2019]

@@

Several previous systematic review of observational studies examining the effect of lipids[@anstey2015] and lipid-regulating agents[@chu2018;@poly2020c] on dementia outcomes have been performed. However, these reviews have several limitations. Many did not consider grey literature sources (see Section \@ref(diverse-sources-preprints)). Additionally, many of the reviews of observational studies did not perform any risk-of-bias assessment[@chu2018b] or used an outdated assessment tool.[@anstey2015;@poly2020c]

### 2021-09-20 02-Chp-Systematic-Review-Tools.Rmd
End of day:

### Limitations of `medrxivr`

@@

Allowing for a two year lag, previous work has found that two-thirds of bioRxiv preprints were published in a peer-reviewed journal,[@abdill2019b] indicating that s not-insignificant number of preprints are never publishe but are accessible as preprints.

>>>>

### Limitations of `medrxivr` {#medrxivr-limitations}

@@

```{r, include=FALSE}
med_res <-
  # Use snapshot from July 2021
  medrxivr::mx_search(medrxivr::mx_snapshot("ccedfb8a44304b9fba4e3ba518a8ce4ed2294770"),
                      "*",
                      from_date = "2019-07-01",
                      to_date = "2019-08-01") %>%
mutate(pub_ind = ifelse(published == "NA", 0, 1)) %>%
  group_by(pub_ind) %>%
  count()

published <- med_res$n[2]
publication_n <- sum(med_res$n)
publish <- paste0(num_to_text(published,T)," (", round(published/publication_n*100,1),"%)")
```

Using `medrxivr` an analysis of the publication rate for medRxiv preprints was performed (see Appendix \@ref(appendix-sys-rev-tools)). `r publish` of the `r publication_n` records posted on medRxiv in July 2019 were published by 30th July 2021 (i.e. allowing for a two-year lag between preprint posting and publication). This finding agrees with previous work demonstrating that two-thirds of bioRxiv preprints are published in a peer-reviewed journal within two years of posting,[@abdill2019b] indicating that a non-insignificant number of preprints are never formally published but remain accessible as preprints.

<!-- TODO replicate this analysis -->

### 2021-09-20 03-Chp-Systematic-Review.Rmd
End of day:

<!-- TODO Extra studies to include: -->
<!-- * Smeet et al. reference in the CPRD analysis -->
<!-- * Larsson - 10.1136/bmj.j5375 [@larsson2017b] -->
<!-- * Statins and the risk of dementia Jick -->

@@

@@

Eligible studies defined dementia according to recognised criteria, for example the National Institute of Neurological Disorders and Stroke Association-Internationale pour la Recherche en l'Enseignement en Neurosciences (NINDS-AIREN), International Classification of Diseases (ICD), or Diagnostic and Statistical Manual of Mental Disorders (DSM) criteria. <!-- TODO CITATION NEEDED --> <!-- TODO do i actually want to include MCI? -->

@@

The use of evidence maps is becoming increasingly common to explore the distibution of research cohorts included in a systematic review.<!-- TODO CITATION NEEDED --> As such, each individual cohort contibuting to the evidence base was quantified and visualised on a world map.

@@

Of the 500 random records screened to ensure the accuracy of the study design filters, no eligible records were identified. Many of those excluded by the filters were basic science studies, commentaries or educational articles. <!-- TODO CITATION NEEDED -->

@@

A common theme across the evidence base was a lack of data on the association of vascular dementia. This is particularly interesting given that lipids and statins are primarily related to vascular disease. There is the potential that studies encountered similar difficulties in address the unexpected results observed in the CPRD analysis in Chapter \@ref(cprd-analysis-heading), likely due to confounding by indication, and so may suffer from the "file-drawer effect". <!-- TODO CITATION NEEDED --> For vascular dementia, few Mendelian randomisation studies examined this outcome, primarily because of the absence (until recently) of genome wide association studies, which are used in two sample summary Mendelian randomisation studies.

@@

While conducting this review, I identified several previous systematic reviews of this topic.[@chu2018; @yang2020; @muangpaisan2010; @poly2020;@kuzma2018a] However, this review is the first to use established domain based assessments tools (for example, the RoB 2 tool for randomized controlled trials)[@sterne2019] to assess the risk of bias in included studies, and explore the heterogeneity of results across different levels of risk of bias levels. Some previous reviews did assess risk of bias, but used non-domain based assessment tools, such as the Newcastle-Ottowa scale. <!-- TODO CITATION NEEDED -->

@@

<!-- IDEA Put upSet plot here - though this will likely now be in Georgia's dissertation -->

<!-- An upset plot shows the total size of each set (in this case, the set of included studies in each review) in the bottom left hand bar plot. For example, the XXXX review includes XXXX studies. The alternative is to have a barplot showing the total cumulative number of records over the years, using our set as the master, with the bars coloured by the number of records included in 1/2/3/4 reviews. The information below the bar axis could then show the number of reviews published in that year, or alternative, you could have an upsidedown bar to show cumulative number of reviews on this topic. -->

@@

@@

medRxiv grew out of the Epidemiology and Clinical Trials categories of the 
<!-- TODO Complete above paragraph -->

The small number of studies return by the searches (or the absence of any hits in the medRxiv database - see Figure \@ref(fig:test)) is due to the timing of the preprint searches. The searches for this review were performed in mid-July 2019, but the first medRxiv preprint was registered on 25th June 2019. As such, at the point it was searched, the medRxiv database contained only a small number of records.

@@

<!----------------------------------------------------------------------------->
```{r preprintGrowthSetup, include=FALSE}
```

(ref:preprintGrowth-cap) __Growth of preprint repositories over time__ - Given the relative sizes of the preprint repositories at the time the searches for this review were conducted (bioRxiv n= `r n_at_search["bio"]`, medRxiv n = `r n_at_search["med"]`), the relative number of hits returned by each is expected.

@@

```{r preprintGrowth, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:preprintGrowth-cap)', out.width='100%', fig.scap='(ref:preprintGrowth-scap)'}
knitr::include_graphics(file.path("figures/sys-rev/preprint_growth.png"))
```
<!----------------------------------------------------------------------------->
<!-- TODO Include figure here showing growth of preprint database size, and cite studies detailing increasing acceptance as a valid form of evidence.  -->

@@

One of the strenghts of this review is it's inclusion of MR studies as a source of evidence.

@@

<!-- However, new developments such as automated screening would allow for a reduced need for personnel to work on these things. <!-- TODO CITATION NEEDED - Cite Triccios new paper here -->

@@

One particular limitiation with regards to the risk of bias assessment is the fact that the ROBINS-E assessments were performed without the tool being finalised. This meant that there were no signalling questions to guide the domain-level risk of bias assessment, which may have influenced the accuracy with which domain-level judgements were assigned. However, there is no published empirical evidence supporting the need for signalling questions, and assessment of inter-rater reliability across the different tools did not indicate a specific problem with the ROBINS-E assessments. In fact, low agreement was common across the tools, though this is expected based on the available literature. <!-- TODO CITATION NEEDED -->

>>>>

<!-- TODO Extra studies to include: -->
<!-- * Larsson - 10.1136/bmj.j5375 [@larsson2017b] -->
<!-- * Statins and the risk of dementia Jick -->

@@

<!-- TODO Search for MCI -->

@@

Eligible studies defined dementia according to recognised criteria, for example the International Classification of Diseases (ICD), National Institute of Neurological Disorders and Stroke Association-Internationale pour la Recherche en l'Enseignement en Neurosciences (NINDS-AIREN), or Diagnostic and Statistical Manual of Mental Disorders (DSM) criteria. <!-- TODO CITATION NEEDED -->

@@

Evidence maps are useful way to explore the distribution of research cohorts included in a systematic review.[@saran2018] As such, the location of each individual study contributing to the evidence base was quantified and visualised on a world map.

@@

Of the 500 random records screened to ensure the accuracy of the study design filters, no eligible records were identified. Many of those excluded by the filters were basic science studies, commentaries or educational articles.

@@

A common theme across the evidence base was a lack of data on the association of vascular dementia. This is particularly interesting given that lipids and statins are primarily related to vascular disease. There is the potential that studies encountered similar difficulties in address the unexpected results observed in the CPRD analysis in Chapter \@ref(cprd-analysis-heading), likely due to confounding by indication, and so may suffer from the "file-drawer effect".[@rosenthal1979] For vascular dementia, few Mendelian randomisation studies examined this outcome, primarily because of the absence (until recently) of genome wide association studies, which are used in two sample summary Mendelian randomisation studies.

@@

While conducting this review, I identified several previous systematic reviews of this topic.[@chu2018; @yang2020; @muangpaisan2010; @poly2020;@kuzma2018a] However, this review is the first to use established domain based assessments tools (for example, the RoB 2 tool for randomized controlled trials)[@sterne2019] to assess the risk of bias in included studies, and explore the heterogeneity of results across different levels of risk of bias levels. Some previous reviews did assess risk of bias, but used non-domain based assessment tools, such as the Newcastle-Ottowa scale.[@anstey2015; @poly2020]

@@

@@

```{r preprintGrowthSetup, include=FALSE}
```

@@

Three relevant preprints were identified

medRxiv grew out of the Epidemiology and Clinical Trials categories of the bioRxiv preprint server. The small number of studies return by the searches (or the absence of any hits in the medRxiv database - see Figure \@ref(fig:prisma-flow-fig)) is due to the timing of the preprint searches. The searches for this review were performed in mid-July 2019, but the first medRxiv preprint was registered on 25th June 2019. As such, at the point it was searched, the medRxiv database contained only a small number of records (n=`r n_at_search["med"]`).

Of the three identified preprints, two were subsequently published as of September 2020. This fits well with the analysis presented in Section \@ref(medrxivr-limitations) that, allowing for a two-year lag, approximately two-thirds of preprints are published.

@@

<!----------------------------------------------------------------------------->
(ref:preprintGrowth-cap) __Growth of preprint repositories over time__ - Given the relative sizes of the preprint repositories at the time the searches for this review were conducted (bioRxiv n= `r n_at_search["bio"]`, medRxiv n = `r n_at_search["med"]`), the relative number of hits returned by each is expected.

@@

```{r preprintGrowth, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:preprintGrowth-cap)', out.width='100%', fig.scap='(ref:preprintGrowth-scap)'}
knitr::include_graphics(file.path("figures/sys-rev/preprint_growth.png"))
```
<!----------------------------------------------------------------------------->
<!-- TODO Cite studies detailing increasing acceptance as a valid form of evidence.  -->

@@

One of the strengths of this review is it's inclusion of MR studies as a source of evidence.

@@

<!-- However, new developments such as automated screening would allow for a reduced need for personnel to work on these things. [@pham2021] -->

@@

One particular limitiation with regards to the risk of bias assessment is the fact that the ROBINS-E assessments were performed without the tool being finalised. This meant that there were no signalling questions to guide the domain-level risk of bias assessment, which may have influenced the accuracy with which domain-level judgements were assigned. However, there is no published empirical evidence supporting the need for signalling questions, and assessment of inter-rater reliability across the different tools did not indicate a specific problem with the ROBINS-E assessments. In fact, low agreement was common across the tools, though this is expected based on the available literature.[@jeyaraman2020]

### 2021-09-20 front-and-back-matter/99-appendices.Rmd
End of day:

@@

__NEED TO ADD DATA HERE!__

@@

## Copies of papers arising from this thesis

>>>>

## Chapter \@ref(sys-rev-tools-heading) {#appendix-sys-rev-tools}
<!----------------------------------------------------------------------------->

### Code for publication rate analysis

```{r, eval=FALSE}
med_res <-
  # Use snapshot of published status from July 2021
  medrxivr::mx_search(
    medrxivr::mx_snapshot("ccedfb8a44304b9fba4e3ba518a8ce4ed2294770"),
    query = "*",
    from_date = "2019-07-01",
    to_date = "2019-08-01"
  ) %>%
  # Create indicator to show which records have been published
  mutate(pub_ind = ifelse(published == "NA", 0, 1)) %>%
  # Group by indicator variable and count
  group_by(pub_ind) %>%
  count()

@@

<!-- TODO __NEED TO ADD DATA HERE!__ -->

@@

## Copies of papers arising from this thesis {#published-papers}
